### 2018-11-28 2018_nips_vigil_poster/main.tex
update vigil poster

\headerbox{The MAC Model ~\cite{hudson2018compositional}}{name=double-pendulum, column=0, below=abstract}{
	\begin{figure}[H]
		\centering
		\subfloat[]{{
				\includegraphics[width=0.35\textwidth]{../img/mac_cell.pdf}
				\label{subfig:pendulum_picture}
		}}

		\caption{The MAC cell ~\cite{hudson2018compositional}}
		\label{fig:pendulum}
	\end{figure}

@@

@@

\headerbox{Transfer Learning - Experiments}{name=dataset, column=1}{

Along with CLEVR, the authors~\cite{johnson2017clevr} introduced  CLEVR-CoGenT (Compositional Generalization Test, CoGenT in short), with a goal of evaluating how well the models can generalize, learn relations and compositional concepts.
This dataset is generated in the same way as CLEVR, with two conditions, A and B. as shown in Table 2.

@@

	\begin{table}[H]
	\centering
	\scalebox{0.9}{
	\caption{CLEVR \& CoGenT accuracies for the MAC \& S-MAC models. The [Training] column indicates wall times and final accuracies on the training set. For fine-tuning, we use 30k samples of the test set, and kept the remainder for testing. The [Fine-tuning] column reports the used sub-set (30k samples) and the final accuracies on this sub-set during training. The [Test] column reports the used set and the obtained test accuracies. If no fine-tuning was done, the whole indicated set was used for testing.}
	\begin{tabular}{lllllllll}
		\toprule
		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} & \multicolumn{2}{c}{Test} & \multirow{2}{*}{Row} \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] & \\
		\midrule
		MAC & CLEVR  & 30:52  & 96.70 & --   & --  & CLEVR    & 96.17         & (a) \\
		\cmidrule{1-8}
		\cmidrule{1-8}

@@

	\end{tabular}}
	\label{tab:data_properties}
\end{table}
}

\headerbox{MAC limitations on CLEVR}{name=baseline, column=1, below=dataset}{

	\begin{figure}[H]
	\centering
	\subfloat[]{{
			\includegraphics[width=0.6\textwidth]{../img/fail_mac_cogent_b_shape.png}
			\label{subfig:pendulum_picture}
	}}

	\caption{The question reads as: \textit{There is a large gray thing that is on the right side of the big gray cylinder left of the large ball that is on the right side if the cyan rubber sphere; what is its shape?}}
	\label{fig:fail_mac_shape}
\end{figure}
	\begin{figure}[H]
	\centering
	\subfloat[]{{
			\includegraphics[width=0.6\textwidth]{../img/fail_mac_cogent_b_color.png}
			\label{subfig:pendulum_picture}
	}}

	\caption{The question reads as: \textit{There is a tiny block behind the rubber thing that is right if the small brown rubber cylinder that is in front of the yellow metal cylinder; what color is it?}}
    \label{fig:fail_mac_color}
\end{figure}

>>>>

\headerbox{The MAC Model ~\cite{hudson2018compositional}}{name=double-pendulum, column=0, below=abstract}{
	\begin{figure}[H]
		\centering

		\includegraphics[width=0.35\textwidth]{../img/mac_cell.pdf}
		\label{subfig:pendulum_picture}
		\caption{The MAC cell ~\cite{hudson2018compositional}}
		\label{fig:pendulum}
	\end{figure}

@@

	\item[$\bullet$] Simplifications results in a 10\% speed up in training time.

@@

\headerbox{Datasets - CLEVR and CoGenT}{name=dataset, column=1}{
The CLEVR task:
		\begin{figure}[H]
		\centering
		\includegraphics[width=0.33\textwidth]{../img/teaser.jpg}
	    \end{figure}

    \begin{description}
    	\centering
    	\item[$\cdot$] \textit{How many objects are either small cylinders or red things?}

   \begin{description}
   	\item[$\bullet$]Along with CLEVR, the authors~\cite{johnson2017clevr} introduced  CLEVR-CoGenT 
   	\item[$\bullet$] The goal is to evaluate how well the models can generalize, learn relations and compositional concepts.
   	\item[$\bullet$] This dataset is generated in the same way as CLEVR, with two conditions, A and B. as shown in Table 2.

@@

\headerbox{Transfer Learning - Experiments}{name=transfer, column=1, below=dataset}{

CLEVR \& CoGenT accuracies for the MAC \& S-MAC models:
	\begin{table}[H]
	\centering
	\scalebox{0.9}{
	\begin{tabular}{lllllllll}
		\toprule
		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} & \multicolumn{2}{c}{Test} & \multirow{2}{*}{Row} \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] & \\
		\midrule
		MAC & CLEVR  & 30:52  & 96.70 & --   & --  & CLEVR    & 96.17         & (a) \\
		\cmidrule{1-8}
		\cmidrule{1-8}

@@

	\end{tabular}}
	\label{tab:data_properties}
\end{table}

\begin{description}
	\item[$\bullet$] The [Training] column indicates wall times and final accuracies on the training set.
	\item[$\bullet$] The [Fine-tuning] column reports the used sub-set (30k samples) and the final accuracies on this sub-set during training
	\item[$\bullet$] Experiments can be reproduced by following the \textbf{mi-prometheus}  documentation
\end{description}

\headerbox{MAC drawbacks on CLEVR}{name=baseline, column=1, below=transfer}{

	\begin{figure}[H]
	\centering
	\subfloat[]{{
			\includegraphics[width=0.6\textwidth]{../img/fail_mac_cogent_b_shape.png}
			\label{subfig:pendulum_picture}
	}}
	\label{fig:fail_mac_shape}

\end{figure}

\begin{description}
	\item[$\bullet$] The question reads as: \textit{There is a large gray thing that is on the right side of the big gray cylinder left of the large ball that is on the right side if the cyan rubber sphere; what is its shape? Predicted answer: Cylinder - Truth: Cube}
